|

### 2021-11-14 07-Chp-Triangulation.Rmd
working triangulation framework

@@

```{r biasDirectionPlots, include = F}
```

@@

>>>>

<!----------------------------------------------------------------------------->
(ref:biasDirectionSingle-cap) Bias direction plot for a single study showing the predicted direction of bias in each domain. Additive biases are characterised using arrows, while the proportional biases are denoted using $<$ and $>$. A question mark indicates that the direction of bias was unpredictable.

(ref:biasDirectionSingle-scap) Bias direction plot for a single study
```{r biasDirectionSingle, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:biasDirectionSingle-cap)', out.width='100%', fig.scap='(ref:biasDirectionSingle-scap)'}
knitr::include_graphics(file.path("figures/misc/UoBcrest.pdf"))
```
<!----------------------------------------------------------------------------->

@@

```{r ldlAdBIAMA, include = F}
```

@@

<!----------------------------------------------------------------------------->
(ref:fpLdlAd-cap) __shortcap:__

(ref:fpLdlAd-scap) shortcap

```{r fpLdlAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAd-cap)', out.width='100%', fig.scap='(ref:fpLdlAd-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad.png"))
```
<!----------------------------------------------------------------------------->
